Gaia's constraints on the extremely massive ($\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-20 VFTS682_APJL.tex
more caveats and some smoothing

The right panel shows the distributions in flight direction for these
stars: $\theta$ is the angle between the projected radial direction from the
center of R136 to each star and its proper motion relative to
R136 (see also \Figref{fig:main}). Dynamical ejections from the
cluster should %are expected to
produce
close to radial ejections, i.e.~$\theta\simeq0$. On this panel, the green band highlights
the range of angles corresponding to an opening angle around the
radial direction of 45\,degrees. The direction of motion of VFTS682 is
poorly constrained because of the large errors on the proper motion
components both in HST and \emph{Gaia} data, but
it is consistent with dynamical ejection from R136. We note that
VFTS72 has a small radial velocity, while VFTS16 (and possibly VRTS682) has
large peculiar radial velocity and therefore accurate distances are
needed to contrain the flight direction in three dimensions.

>>>>

The right panel shows the distributions in projected flight direction for these
stars: $\theta$ is the angle between the projected radial direction from the
center of R136 to each star and its projected relative proper motion (see also \Figref{fig:main}). Dynamical ejections from the
cluster should %are expected to
produce
close to radial ejections, i.e.~$\theta\simeq0$ \todo{this is only
  true for small RV}. On this panel, the green band highlights
the range of angles corresponding to an opening angle around the
projected radial direction of 45\,degrees. The direction of motion of VFTS682 is
poorly constrained because of the large errors on the proper motion
components both in HST and \emph{Gaia} data, but
it is consistent with dynamical ejection from R136. We note that
VFTS72 has a small radial velocity, while VFTS16 (and possibly VRTS682) has
large peculiar radial velocity and therefore accurate distances are
needed to contrain the flight direction in three dimensions.
